MJSAI: Designing a Sound, Configurable, Efficient, and Pushdown Monadic Static~Analyzer for JavaScript

### 2014-12-13 cs252r-fa14-writeup/paper.tex
Add a couple macros and fix up section headings
finish picture

@@

@@

\section{Design}
\subsection{Pushdown Analysis in \maam{}}

@@

We can now describe a AAM-style approach for producing a pushdown abstract
machine from a concrete CEK machine:
\begin{enumerate}
\item Break recursion in the environment, caused by closures, with a store,
  which maps addresses to values, and change the environment to map variables to
  addresses.
\item Break recursion in the continuation stack by creating a
  continuation-store, which maps continuation-addresses to either the halt frame
  or a pair of a frame and a continuation-address.
\item Add a memo table which maps a triplets of a command, an environments, and
  a store to a value.
\end{enumerate}

\begin{figure}
\centering
% \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3cm,
%   thick,main node/.style={circle,fill=blue!20,draw,font=\sffamily\Large\bfseries}]

%   \node[main node] (1) {\cek{c}{$\rho$}{$\kappa$}};
%   \node[main node] (2) [right of = 1] {\cesk{c}{$\rho$}{$\sigma$}{$\kappa$}};
%   \node[main node] (3) [right of = 2] {\cessk{c}{$\rho$}{$\sigma$}{$\kappa\sigma$}{$\kappa$}};
%   \node[main node] (4) [right of = 3] {\cesskc{c}{$\rho$}{$\sigma$}{$\kappa\sigma$}{$\kappa$}{$\Chi$}};

%   \path[->]
%     (1) edge (2) edge (3) edge (4);

% \end{tikzpicture}
\caption{An AAM-style approach for producing a pushdown abstract machine} \label{fig:M1}
\end{figure}

\subsection{A \js{} Analysis in \maam{}}

>>>>

\newcommand{\partto}{\rightharpoonup}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Machine Configurations

\newcommand{\cek}[3]{\langle #1, #2, #3 \rangle}
\newcommand{\cesk}[4]{\langle #1, #2, #3, #4 \rangle}
\newcommand{\cessk}[5]{\langle #1, #2, #3, #4, #5 \rangle}
\newcommand{\cesskc}[6]{\langle #1, #2, #3, #4, #5, #6 \rangle}

@@

\section{Design}
\subsection{Pushdown Analysis in MAAM}

@@

We can now describe a \aam{}-style approach for producing a pushdown abstract
machine from a concrete CEK machine:
\begin{enumerate}
\item Break recursion in the environment, caused by closures, with a store,
  which maps addresses to values, and change the environment to map variables to
  addresses.
\item Break recursion in the continuation stack by creating a
  continuation-store, which maps continuation-addresses to either the halt frame
  or a pair of a frame and a continuation-address.
\item Add a memo table which maps a triplets of a command, an environments, and
  a store to a value.
\end{enumerate}

\begin{figure}
\centering

\begin{equation*}
\begin{array}{c c l c l}
  c            &:& Exp        && \\
  \rho         &:& Env        &=& Var   \partto Addr \\
  \sigma       &:& Store      &=& Addr  \partto Value \\
  \kappa\sigma &:& KStore     &=& KAddr \partto Frame \times KAddr \\
  \kappa       &:& KAddr      && \\
  \chi         &:& Cache      &=& Exp \times Store \times Env \partto Value
\end{array}
\end{equation*}

\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.5cm,
  thick,main node/.style={font=\sffamily\bfseries}]

  \node[main node] (101) at (0, 1)
    {$\cek{c}{\rho}{\kappa}$};
  \node[main node] (102) [right of = 101]
    {$\cesk{c}{\rho}{\sigma}{\kappa}$};
  \node[main node] (103) [right of = 102]
    {$\cessk{c}{\rho}{\sigma}{\kappa\sigma}{\kappa}$};
  \node[main node] (104) [right of = 103]
    {$\cesskc{c}{\rho}{\sigma}{\kappa\sigma}{\kappa}{\chi}$};

  \path[->]
    (101) edge node {Step 1} (102)
    (102) edge node {Step 2} (103)
    (103) edge node {Step 3} (104);

\end{tikzpicture}
\caption{An AAM-style approach for producing a pushdown abstract machine} \label{fig:M1}
\end{figure}

\subsection{A JavaScript Analysis in MAAM}
